Project Light

### 2015-08-25 paper/paper.tex
outline + gitignore

@@

@@

\section{Implementation}
\label{sec:contiki_integration}

\begin{itemize}
	\item Android app - functionality, flashlight, limitations
	\item contiki process - functionality, rtimer?, kmeans?, limitations
	\item driver wrapper to delay link layer initialization until key is initialized
\end{itemize}

@@

\begin{itemize}
	\item measure and evaluate maximum transmission speed, error rate
	\item is hamming code necessary (worth the doubled length) or CRC alone sufficient
	\item does the transmission rate have to be variable?
\end{itemize}

@@

\begin{itemize}
	\item bidirectional communication using the LEDs of the mote (and maybe camera)
	\item 802.15.4 dongle to verify transmission (and do further initialization)
\end{itemize}

>>>>

\begin{itemize}
	\item short introduction internet of things
	\item some words about contiki
	\item current security and key distribution situation
	\item idea of transmitting keying material using light and phone app
	\item setup (android device/app, mote with light sensor)
\end{itemize}

@@

\begin{itemize}
	\item phases of protocol
	\begin{itemize}
		\item calibration
		\item synchronization
		\item initialization
		\item data sending
		\item validation
	\end{itemize}
\end{itemize}

@@

\section{Contiki Integration}
\label{sec:contiki_integration}

@@

@@
